---
title: "Ggplot_Themes"
author: "Ajay Kumar"
date: "August 22, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# An introduction to Themes

 - The appearance of non-data elements is
 controlled by themes.
 
 - Themes give you control over 
   - Fonts in all parts of the plot.
   - Title
   - Axis tick labels
   - Axis labels
   - Strip labels
   - Legend key  labels
   - Background

  `Ggplot` takes a different approach to building graphs
  compared to base and lattice graphics.
  - When creating the plot, one can determine how to display the    data 
  - After creating the plot one can edit every detail of      
  rendering it using the `theming` system.
  
# Built in Themes

`ggplot2` has 2 built-in themes. The default *`theme_grey()`*
uses a light grey background with white gridlines. The second
theme *`theme_bw()`* has a traditional white background
and dark grey gridlines. Themes can be applied in
two ways.
 - Using the `theme_set()` function globally
 - Or using the above function inside an individual plot 
   function.
   
# Theme elements and element functions

There are four types of built in element 
functions

 - Text:
 
 *`element_text()`* draws labels and headings.
 Some examples are shown below
 
```{r Theme_text}

library(ggplot2)
library(grid)
library(gridExtra)
# get the mpg variable from the mtcars dataset
mpg <- mtcars$mpg
m <- length(mpg)
# draw histogram of mpg variable from mtcars data
splot <- qplot(x = 1:m, y = mpg, 
               geom = "point", colour = I("red"),
               xlab = "Obs number", ylab = "Mpg")

splot2 <- splot + ggtitle("Title") + 
              theme(plot.title = element_text(size = 15))

splot3 <- splot + ggtitle("New Title") +
            theme(plot.title = element_text(size = 15, 
                  colour = "red"))

splot4 <- splot + ggtitle("Newer Title") +
            theme(plot.title = element_text(size = 15, 
                  hjust = 1))

splot5 <- splot + ggtitle("Another Title") +
         theme(plot.title = element_text(size = 15,
                  face = "italic"))

splot6 <- splot + ggtitle("Last Title") + 
  theme(plot.title = element_text(size = 15,
        angle = 180))

grid.arrange(splot, splot2, splot3,
             splot4, splot5, splot6, nrow = 3,
             ncol = 2)

```
 
 - Lines and Segments
 - Rectangles
 - Blanks
 
Code snippets will soon be uploaded. 
  
  
  
  
  
  
