---
title: "Ggplot_Notes"
author: "Ajay Kumar"
date: "August 8, 2016"
output: html_document
---

The matrial in this section is covered online 
Refer the `ggplot2` documentation. I have also
referred to Hadley Wickham's book on `ggplot2`

# Building scatterplots

Below is a plot of the displacement vs the 
highway mpg variable coloured by a third variable
cylinder. There are many methods of making this plot.

 1. With `qplot`

```{r Qplot}
library(ggplot2)
library(scales)
library(grid)
library(gridExtra)

p <- qplot(disp, hwy, data = mpg, 
        colour = as.factor(cyl))

```

  2. With `ggplot`
  
```{r ggplot}

p <- ggplot(data = mpg, aes(x = disp, y = hwy,
                            colour = cyl)) +
       geom_point
p + scale_color_hue("Cylinder")
```
  
  
## Behind a scatterplot

We map the X and Y co-ordinates. In addition
every point has a size, colour and a shape. 
These are called `aesthetics`. We map aesthetics
to data.  

A scatterplot is represented by a `geom` called
`point()`. Other kinds of `geoms` can be used
to display suitable plots.

The data needs to be converted from it's original
units to things that a computer can understand. 
We need to provide a mapping to pixels which 
can be read by a computer. 

# Building Multiple Time Series

The technique explains how to compare multiple
time series correctly. 
The data used is the economics dataset.

```{r Time_Series}
library(reshape2)
emp <- melt(data = economics, id = "date",
            measure.vars  = c("unemploy", "uempmed"))

qplot(date, value, data = emp, geom = "line") +
  facet_grid(variable ~., scales = "free_y")

```



